Synthesizing Quotient Lenses

### 2018-03-13 papers/QuotientLenses/main.tex
partial pass over section 5

Having identified QREs as a natural way of specifing equivalence relations on
regular expressions, a natural next step in defining quotient lenses is to map
between two QREs via a bijection between their; this is our
approach in defining {\em QRE lenses}.

More concretely, in order to define a language of QRE lenses, our approach is
to (1) define a language of bijections (Section \ref{subsec:bijective-lenses}),
and then (2) add quotients by allowing canonizers to be prepended or postpended
to bijections and (3) allowing composition of such quotient lenses via the
regular operators and functional composition
(Sections \ref{subsec:qre-lenses-syntax} and \ref{subsec:qre-lenses-semantics}).

However, we also have a secondary objective, which is to support synthesis of
lenses: When provided with QREs describing the source and target languages, we
would like to be able to generate quotient lenses automatically. One way to do
that is to generate canonizers $\canonize(Q_1)$ and $\canonize(Q_2)$ from QREs
$Q_1$ and $Q_2$ and then to synthesize bijective lenses between the kernel
languages for $Q_1$ and $Q_2$.

Unfortunately, the composition of two such quotient lenses does not have have
the form of a bijective lens with canonizers at the edges. Hence, an important
technical question is whether we give up expressiveness if we restrict
ourselves to this form. Thankfully, this turns out not to be an issue if
the bijections that we use to define QRE lenses are derived using a particular
set of combinators that we describe in the next section.

>>>>

Having identified QREs as a natural way of specifing equivalence relations on
regular expressions, a natural next step in defining quotient lenses is to map
between two QREs via a bijection between their kernels; indeed, this approach
is the one we adopt in defining {\em QRE lenses}.
More concretely, to define a language of QRE lenses, we
(1) define a language of bijections (Section \ref{subsec:bijective-lenses}),
(2) add quotients by allowing canonizers to be prepended or postpended
to bijections, and 
(3) allow composition of such quotient lenses via the
regular operators and functional composition
(Sections \ref{subsec:qre-lenses-syntax} and \ref{subsec:qre-lenses-semantics}).

However, we also have a secondary objective, which is to support lens
synthesis. When provided with QREs describing the source and target
languages, we would like to be able to generate quotient lenses
automatically. One way to achieve that goal is to generate canonizers
$\canonize(Q_1)$ and $\canonize(Q_2)$ from QREs $Q_1$ and $Q_2$ and
then to synthesize bijective lenses between the kernel languages for
$Q_1$ and $Q_2$.
Unfortunately, the composition of two such quotient lenses does not have 
the form of a bijective lens with canonizers at the edges. Hence, an important
technical question is whether we give up expressiveness if we restrict
ourselves to this form. 
Thankfully, we can show that there is no loss of expressiveness if
the bijections used to define QRE lenses are derived with a particular
set of combinators.  We describe these combinators next.
